---
title: "simpleRegress"
author: "Paulo poblete"
date: "10 - 20 - 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26



```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE,interval = "prediction")
```

## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```


As per the data above, we can see that the multiple R sq is bigger in this one in comparison with the other plot with the LENGTH and CHEST. Our adjusted R sq is also a little bit bigger here. Our residual standard error in this model is 4.9 which is smaller compared to the 5.3 of the other plot which contains LENGTH and CHEST.  

```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```

Compared to the other 2 models above, respectively, LENGTH and NECK, and LENGTH and CHEST. This model seems to has similarities with the first model in regards to its residual standard error and adjusted r sq value. This model are about the same and WEIGHT did not give us a significant change to our values. 


